---
title: "PI Summit Figures"
author: "Brandon D. Gallas"
date: "5/5/2021"
output:
  pdf_document: default
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = FALSE)

# I set cache = TRUE to save figures as separate files.
# However, if cache = TRUE there is another (primary) consequence.
# If a code chunk has not changed, it will not be run (ave time).
# This means you may not see changes earlier in the file (dangerous/confusing).
# https://bookdown.org/yihui/rmarkdown-cookbook/cache.html
# knitr::opts_chunk$set(echo = FALSE, cache = TRUE)

# This command does what I want. It creates an html or pdf of the whole
# document while also creating the figures 
# https://stackoverflow.com/questions/27992239/
#    knitr-include-figures-in-report-and-output-figures-to-separate-files
knitr::opts_chunk$set(fig.path = 'figures/', dev = c('png', 'pdf'))

# This knitr command is useful for debugging.
# It stops compiling early to produce the output.
# knitr::knit_exit()

```

This file produces the figures presented at Pathology
Informatics, 6 May 2021. There are minor differences compared to the actual
presentation as annotations and pathologist information were being collected
continuously.

Furthermore, in the "Scatter plot" sections, the grouping of scores into bins
based on the mean sTIL density has changed. For the Pathology Informatics talk,
it was determined from all the readers using the caMicroscope platform.
Now, the bins are determined in two ways: from all the data and from the panel.

```{r init Data And Libs}

# Specify the filter date.
filterDate <- "2021-05-05 00:00:00 EST"

# Filter the data by date
mrmcDF.pilot <- HTT::pilotHTT
mrmcDF.pilot <- mrmcDF.pilot[mrmcDF.pilot$createDate < filterDate, ]

# Filter data by modality
mrmcDF.camic <- mrmcDF.pilot[mrmcDF.pilot$modalityID == "camic", ]
mrmcDF.pathp <- mrmcDF.pilot[mrmcDF.pilot$modalityID == "pathp", ]
mrmcDF.eedap <- mrmcDF.pilot[mrmcDF.pilot$modalityID == "eedap", ]

# Refactor readerID
mrmcDF.camic$readerID <- factor(as.character(mrmcDF.camic$readerID))
mrmcDF.pathp$readerID <- factor(as.character(mrmcDF.pathp$readerID))
mrmcDF.eedap$readerID <- factor(as.character(mrmcDF.eedap$readerID))

```

```{r meanVarByCase.R}

# Focus on caMicroscope data
modalityID <- "camic"
mrmcDF <- mrmcDF.pilot[mrmcDF.pilot$modalityID == modalityID, ]

# Split the data by caseID
mrmcByCase <- split(mrmcDF, mrmcDF$caseID)

# Calculate the stats by case
statsByCase <- lapply(mrmcByCase, HTT::doStatsByCase)
statsByCaseDF <- do.call(rbind, statsByCase)

# Filter out missing data (data without enough observations for calculating the mean or variance)
index <- !is.na(statsByCaseDF$scoreVar)
statsByCaseDF <- statsByCaseDF[index, ]

# Sort the data by the mean
index <- order(statsByCaseDF$scoreMean)
statsByCaseDF <- statsByCaseDF[index, ]

# Identify bins of equal size
index.bin <- (1:10) * length(statsByCaseDF$scoreMean)/10
scoreMean.bin <- statsByCaseDF$scoreMean[index.bin]

# Estimate mean values within the bins
scoreVar.bin <- mean(statsByCaseDF$scoreVar[0:index.bin[1]])
CV.bin <- mean(statsByCaseDF$CV[0:index[1]])
for (i in 2:10) {
  scoreVar.bin <- c(scoreVar.bin, mean(statsByCaseDF$scoreVar[index.bin[i - 1]:index.bin[i]]))
  CV.bin <- c(CV.bin, mean(statsByCaseDF$CV[index.bin[i - 1]:index.bin[i]]))
}

casesLE10 <- statsByCaseDF[statsByCaseDF$scoreMean <= 10, "caseID"]
casesGT10LE40 <- statsByCaseDF[statsByCaseDF$scoreMean > 10 &
                                 statsByCaseDF$scoreMean <= 40 , "caseID"]
casesGT40 <- statsByCaseDF[statsByCaseDF$scoreMean > 40, "caseID"]

```

```{r function.convertMRMCtoDesignByBatch}

convertMRMCtoDesignByBatch <- function(mrmcDF.cur) {

  mrmcDF.cur.ReaderBatches <- split(mrmcDF.cur, list(mrmcDF.cur$readerID, mrmcDF.cur$batch))
  mrmcDF.cur.ReaderBatch.1 <- mrmcDF.cur.ReaderBatches[[1]]

  checkCompleteReaderBatch <- function(mrmcDF.cur.ReaderBatch.1) {

    mrmcDF.cur.ReaderBatch.1$caseID <- factor(mrmcDF.cur.ReaderBatch.1$caseID)
    if (nlevels(mrmcDF.cur.ReaderBatch.1$caseID) == 80) batchComplete <- 1
    if (nlevels(mrmcDF.cur.ReaderBatch.1$caseID) < 80) batchComplete <- 0
    if (nlevels(mrmcDF.cur.ReaderBatch.1$caseID) > 80) {
      print("Unexpected result.")
      browser()
    }
    return(batchComplete)
  }

  designOut <- unlist(lapply(mrmcDF.cur.ReaderBatches, checkCompleteReaderBatch))

  dim(designOut) <- c(nlevels(mrmcDF.cur$readerID), nlevels(mrmcDF.cur$batch))

  designOut <- t(designOut)

}

```

```{r function.showDesignHTT}

showDesignHTT <- function(mrmcDF.cur) {
  
  # Save the default values of the figure margins
  mai.default <- c(1.02, 0.82, 0.82, 0.42)
  mai.cur <- mai.default
  # Increase the value of left margin of the figure
  mai.cur[2] <- 1.5
  par("mai" = mai.cur)

  designOUT <- iMRMC::convertDFtoDesignMatrix(mrmcDF.cur, dropFlag = FALSE)

  x <- 1:nlevels(mrmcDF.cur$caseID)
  y <- 1:nlevels(mrmcDF.cur$readerID)
  image(x, y, designOUT,
        main = paste("Reader progress,", mrmcDF.cur[1, "modalityID"]),
        xlab = "ROIs/Images/Batches", ylab = "",
        yaxt = "n"
  )
  
  axis(side = 2, at = y, labels = FALSE)
  text(par("usr")[1], y, labels = levels(mrmcDF.cur$readerID), pos = 2, xpd = TRUE)
  
  # Add lines separating batches
  lines(c(80.5,80.5), c(0,100))
  lines(c(160.5,160.5), c(0,100))
  lines(c(240.5,240.5), c(0,100))
  lines(c(320.5,320.5), c(0,100))
  lines(c(400.5,400.5), c(0,100))
  lines(c(480.5,480.5), c(0,100))
  lines(c(560.5,560.5), c(0,100))
  lines(c(640.5,640.5), c(0,100))

  # Add lines separating readers  
  for (i in 1:ncol(designOUT)) {
    lines(c(0, 640.5), c(i, i) + 0.5)
  }
  
  par("mai" = mai.default)
  
  designByBatchDF.cur <- convertMRMCtoDesignByBatch(mrmcDF.cur)
  
  print(paste("Total number of observations", nrow(mrmcDF.cur)))
  print(paste("Total number of readers", nlevels(mrmcDF.cur$readerID)))
  print(paste("Total number of completed batches", sum(designByBatchDF.cur)))
  result <- rowSums(designByBatchDF.cur)
  names(result) <- paste("batch00", 1:8, sep = "")
  print(result)

}

```

# Data collected total

```{r totals}

desc.total.obs <- nrow(mrmcDF.pilot)
desc.total.readers <- nlevels(mrmcDF.camic$readerID) +
  nlevels(mrmcDF.pathp$readerID) + nlevels(mrmcDF.eedap$readerID)

```

**Data collection progress**

* Date: `r filterDate`
 
* Across all platforms
  * Total number of observations `r desc.total.obs`
  * Total number of readers = `r desc.total.readers`

\pagebreak

# Data collected caMicroscope

```{r}

showDesignHTT(mrmcDF.camic)

```

\pagebreak

# Data collected PathPresenter

```{r}

showDesignHTT(mrmcDF.pathp)

```

\pagebreak

# Data collected eeDAP

```{r}

showDesignHTT(mrmcDF.eedap)

```

# Coefficient of Variation

```{r meanVarByCase.showCVByMean-Best}

mean.min <- 0
mean.max <- 100
CV.min <- 0
CV.max <- max(statsByCaseDF$CV)

main <- paste(modalityID, ": CV for each ROI ", 
              "(nROI=", nrow(statsByCaseDF), ")", sep = "")

plot(
  statsByCaseDF$scoreMean, statsByCaseDF$CV,
  main = main,
  xlab = "Mean sTIL density",
  ylab = "CV sTIL density",
  xlim = c(mean.min, mean.max),
  ylim = c(CV.min, CV.max),
  col = rgb(0, 0, 0, 0.2)
)

# Plot the average for each 10% bin of the data
lines(c(0,scoreMean.bin[1]), c(1, 1) * CV.bin[1], lwd = 5)
for (i in 2:length(scoreMean.bin)) {
  lines(c(scoreMean.bin[i - 1],scoreMean.bin[i]), c(1, 1) * CV.bin[i], lwd = 5)
}

# Partition the plot into clinically defined regions
lines(c(10, 10), c(0, 1.5), lwd = 3, lty = 2)
lines(c(40, 40), c(0, 1.5), lwd = 3, lty = 2)

text(2.5, 2, paste("nROI", length(casesLE10), sep = "\n"))
text(25, 2, paste("nROI", length(casesGT10LE40), sep = "\n"))
text(70, 2, paste("nROI", length(casesGT40), sep = "\n"))

```

# Mean-Variance Relationship

```{r meanVarByCase.showVarByMean-Best}

mean.min <- 0
mean.max <- 100
var.min <- 0
var.max <- max(statsByCaseDF$scoreVar)

main <- paste(modalityID, ": Variance for each ROI ", 
              "(nROI=", length(statsByCaseDF$CV), ")", sep = "")

plot(
  statsByCaseDF$scoreMean, statsByCaseDF$scoreVar,
  main = main,
  xlab = "Mean sTIL density",
  ylab = "Var sTIL density",
  xlim = c(mean.min, mean.max),
  ylim = c(var.min, 1100),
  col = rgb(0, 0, 0, 0.25)
)

# Plot the average for each 10% bin of the data
lines(c(0,scoreMean.bin[1]), c(1, 1) * scoreVar.bin[1], lwd = 5)
for (i in 2:length(scoreMean.bin)) {
  lines(c(scoreMean.bin[i - 1],scoreMean.bin[i]), c(1, 1) * scoreVar.bin[i], lwd = 5)
}

# Partition the plot into clinically defined regions
lines(c(10, 10), c(0, 100000), lwd = 3, lty = 2)
lines(c(40, 40), c(0, 100000), lwd = 3, lty = 2)

text(2.5, 1000, paste("nROI", length(casesLE10), sep = "\n"))
text(25, 1000, paste("nROI", length(casesGT10LE40), sep = "\n"))
text(70, 1000, paste("nROI", length(casesGT40), sep = "\n"))

```

```{r agreeDensityBRBM-perR.config4}

# In this file we look at the reader-averaged MSD for each reader
# MSD = mean-squared deviation

# Specify the configuration for this analysis

modalityLabel0 <- factor(c(
  "1: camic",
  "2: eedap",
  "3: pathp",
  "4: all",
  "5: all panel"
))

subgroupLabel0 <- factor(c(
  "1: all considered",
  "2: avg. less than or equal to 10",
  "3: avg. greater than 10 and less than or equal to 40",
  "4: avg. greater than 40",
  "5: score.X equal to zero"
))

config0 <- expand.grid(modalityLabel = modalityLabel0, subgroupLabel = subgroupLabel0)

# Run the between-reader analysis for config0[4,]
# modalityLabel = "4: all"
# subgroupLabel = "1: all considered"
resultsByConfig.curr <- HTT::agreeDensityBRBM(
  mrmcDF.pilot,
  config0$modalityLabel[4],
  config0$subgroupLabel[4]
)

```

```{r unpack-resultsByConfig}

# Unpack the key data
modalityLabel <- resultsByConfig.curr$modalityLabel
subgroupLabel <- resultsByConfig.curr$subgroupLabel
modalityID <- resultsByConfig.curr$modalityID
nR <- resultsByConfig.curr$nR
readers <- resultsByConfig.curr$readers
xlim.filter <- resultsByConfig.curr$xlim.filter

mrmcDF <- resultsByConfig.curr$mrmcDF
mrmcBRWM <- resultsByConfig.curr$mrmcBRWM
mrmcByRRWM <- resultsByConfig.curr$mrmcByRRWM
resultsBRWM <- resultsByConfig.curr$resultsBRWM
resultsByRRWM <- resultsByConfig.curr$resultsByRRWM

```

\pagebreak

# Mean-Squared Deviation Per Reader
## All readers, all modalities, All data

```{r resultsPerReader}

# Organize MSD results as a matrix
MSD.RR <- resultsBRWM$MSD
dim(MSD.RR) <- c(nR, nR)
rownames(MSD.RR) <- resultsBRWM$readerID.1[1:nR]
colnames(MSD.RR) <- resultsBRWM$readerID.1[1:nR]

# For every reader.X, average over reader.Y 
MSDperR <- rowMeans(MSD.RR, na.rm = TRUE)

# Start building the data frame
resultsPerReader <- data.frame(readerID = names(MSDperR), MSD = MSDperR)

# Organize nObs results as a matrix
nObs <- resultsBRWM$nObs
dim(nObs) <- c(nR, nR)
rownames(nObs) <- resultsBRWM$readerID.1[1:nR]
colnames(nObs) <- resultsBRWM$readerID.1[1:nR]

# For every reader.X, sum over the observations
rSum.nObs <- rowSums(nObs, na.rm = TRUE)
resultsPerReader$nObs <- rSum.nObs

# Rescale nObs (1, max) to be between 1 and 5
rsum.nObs.scaled <- HTT::lineFromTwoPoints(rSum.nObs, 1, 1, max(rSum.nObs), 5)
resultsPerReader$nObs.scaled <- rsum.nObs.scaled

# Specify the symbol for each profession type
resultsPerReader$pch <- 0
index <- grep("resident", resultsPerReader$readerID)
resultsPerReader[index, "pch"] <- 1
index <- grep("unknown", resultsPerReader$readerID)
resultsPerReader[index, "pch"] <- 2

# Some readers had no paired observations with other readers
# This leads to NaN from rowMeans function. Exclude this data.
resultsPerReader <- resultsPerReader[resultsPerReader$nObs >= 1, ]

```


```{r agreeDensityBRBM-perR.showMSDperReader}

# Prepare for a plot of the reader-average
main <- paste("modality", modalityLabel, "... subgroup", subgroupLabel)
sub <- paste("Largest symbol ==", max(resultsPerReader$nObs), "observations")
xlab <- "reader.X"
ylab <- "The reader-average of MSD given reader.X"

plot(NULL,
     xlim = c(0, nR), ylim = c(0, 850),
     main = main, sub = sub, xlab = xlab, ylab = ylab)

index <- order(resultsPerReader$MSD)
resultsPerReader <- resultsPerReader[index, ]
rownames(resultsPerReader) <- 1:nrow(resultsPerReader)

lines(c(0,nR), c(0,0))
for (i in 1:nR) points(
  i,
  resultsPerReader$MSD[i],
  pch = resultsPerReader$pch[i],
  cex = resultsPerReader$nObs.scaled[i]
)

legend(0, 850, legend = c("Pathologists", "Residents", "Unknown"), pch = 0:2)

print(resultsPerReader)

```

\pagebreak

# Mean-Squared Deviation Per Reader
## PANEL, all modalities, All data

```{r agreeDensityBRBM-perR.panel}

# Run the between-reader analysis for config0[5,]
# modalityLabel = "5: all panel"
# subgroupLabel = "1: all considered"
resultsByConfig.curr <- HTT::agreeDensityBRBM(
  mrmcDF.pilot,
  config0$modalityLabel[5],
  config0$subgroupLabel[5]
)

# This code only works when the document is knit.
# It doesn't work when the code is run like a script.
# Essentially the code chunks named are run.
<<unpack-resultsByConfig>>
<<resultsPerReader>>
<<agreeDensityBRBM-perR.showMSDperReader>>

```

\pagebreak

# Scatter plot: Average Score <= 10

```{r agreeDensityBRBM-MRMC.config9}

# Run the between-reader analysis for config0[9,]
# modalityLabel = "4: all"
# subgroupLabel = "1: all considered"
resultsByConfig.curr <- HTT::agreeDensityBRBM(
  mrmcDF.pilot,
  config0$modalityLabel[9],
  config0$subgroupLabel[9]
)

# This code only works when the document is knit.
# It doesn't work when the code is run like a script.
# Essentially the code chunks named are run.
<<unpack-resultsByConfig>>

```

```{r agreeDensity-MRMC.scatterplot}

# Take the log of the data after adding a small amount to each score
mrmcBRWM$score.X <- log10(mrmcBRWM$score.X + 1)
mrmcBRWM$score.Y <- log10(mrmcBRWM$score.Y + 1)

mean.min <- 0.5
mean.max <- log10(100)

# Determine the frequency table for paired observations
resultBlaAlt <- HTT::getBlandAltmanWithDuplicates(mrmcBRWM)

# Rescale nObs (1, max) to be between 1 and 5
resultBlaAlt$nObs.scaled <- HTT::lineFromTwoPoints(
  resultBlaAlt$nObs, 1, .5, max(resultBlaAlt$nObs), 5
)

# For the scatter plots, make the plot region square
default.par <- par(no.readonly = TRUE)
par(pty = "s")

# Between-reader Symmetrized scatter plot
maxScore <- 10^max(c(mrmcBRWM$score.X, mrmcBRWM$score.Y))
main <- paste("Modality", modalityLabel, "... Subgroup", subgroupLabel)
sub <- paste("n = ", nrow(mrmcBRWM), ", Largest symbol ==", max(resultBlaAlt$nObs), "observations")
plot(10^(resultBlaAlt$x), 10^(resultBlaAlt$y), log = "xy",
     cex = resultBlaAlt$nObs.scaled, col = rgb(0, 0, 0, resultBlaAlt$nObs.scaled/5),
     lwd = 3,
     xlim = c(.5,100), ylim = c(.5,100),
     main = main, sub = sub, xlab = "Score Reader X", ylab = "Score Reader Y")
lines(c(.1,maxScore), c(.1, maxScore))

# Return the plotting parameters to their defaults
par(default.par)

# Do the between-reader, between-modality analysis
limitsOfagreement <- iMRMC::laBRBM(mrmcDF, modalitiesToCompare = c(modalityID, modalityID))
print(limitsOfagreement)

```

\pagebreak

```{r agreeDensityBRBM-MRMC.config10}

# Run the between-reader analysis for config0[10,]
# modalityLabel = "5: all panel"
# subgroupLabel = "2: avg. less than or equal to 10"
resultsByConfig.curr <- HTT::agreeDensityBRBM(
  mrmcDF.pilot,
  config0$modalityLabel[10],
  config0$subgroupLabel[10]
)

# This code only works when the document is knit.
# It doesn't work when the code is run like a script.
# Essentially the code chunks named are run.
<<unpack-resultsByConfig>>
<<agreeDensity-MRMC.scatterplot>>

```

\pagebreak

# Scatter plot: 10 < Average Score <= 40

```{r agreeDensityBRBM-MRMC.config14}

# Run the between-reader analysis for config0[14,]
# modalityLabel = "4: all"
# subgroupLabel = "3: avg. greater than 10 and less than or equal to 40"
resultsByConfig.curr <- HTT::agreeDensityBRBM(
  mrmcDF.pilot,
  config0$modalityLabel[14],
  config0$subgroupLabel[14]
)

# This code only works when the document is knit.
# It doesn't work when the code is run like a script.
# Essentially the code chunks named are run.
<<unpack-resultsByConfig>>
<<agreeDensity-MRMC.scatterplot>>

```

\pagebreak

```{r agreeDensityBRBM-MRMC.config15}

# Run the between-reader analysis for config0[15,]
# modalityLabel = "5: all panel"
# subgroupLabel = "3: avg. greater than 10 and less than or equal to 40"
resultsByConfig.curr <- HTT::agreeDensityBRBM(
  mrmcDF.pilot,
  config0$modalityLabel[15],
  config0$subgroupLabel[15]
)

# This code only works when the document is knit.
# It doesn't work when the code is run like a script.
# Essentially the code chunks named are run.
<<unpack-resultsByConfig>>
<<agreeDensity-MRMC.scatterplot>>
  
```


\pagebreak

# Scatter plot: Average Score > 40

```{r agreeDensityBRBM-MRMC.config19}

# Run the between-reader analysis for config0[19,]
# modalityLabel = "4: all"
# subgroupLabel = "4: avg. greater than 40"
resultsByConfig.curr <- HTT::agreeDensityBRBM(
  mrmcDF.pilot,
  config0$modalityLabel[19],
  config0$subgroupLabel[19]
)

# This code only works when the document is knit.
# It doesn't work when the code is run like a script.
# Essentially the code chunks named are run.
<<unpack-resultsByConfig>>
<<agreeDensity-MRMC.scatterplot>>

```

\pagebreak

```{r agreeDensityBRBM-MRMC.config20}

# Run the between-reader analysis for config0[20,]
# modalityLabel = "5: all panel"
# subgroupLabel = "4: avg. greater than 40"
resultsByConfig.curr <- HTT::agreeDensityBRBM(
  mrmcDF.pilot,
  config0$modalityLabel[20],
  config0$subgroupLabel[20]
)

# This code only works when the document is knit.
# It doesn't work when the code is run like a script.
# Essentially the code chunks named are run.
<<unpack-resultsByConfig>>
<<agreeDensity-MRMC.scatterplot>>
  
```
